### 2023-07-06 paper/sec-analysis.tex
summary
Removed mentions of reduction factor 0.5 which is now unnecessary, unified notation

The profiling method applied to Hessian PDF fits is described in~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre} and is based
on minimizing a goodness-of-fit error function defined as
\begin{equation}
\chi^2 = 
\sum_{i=1}^{N_{\textrm{bin}}} 
\frac{\left(  \mathcal{O}_i^{\rm (exp)}
            + \Gamma_i^{\alpha,\textrm{pd}}
              b_\alpha^{\textrm{(pd)}}
            - \mathcal{O}_i^{\textrm{th}}
            - \Gamma_i^{\beta,\textrm{th}}
              b_\beta^{(\textrm{th})}
     \right)^2
     }{\delta_{{\rm stat},i}^2}
+ \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
+ \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, .
\label{eq:profilingchi2}
\end{equation}
The pseudodata 
$\mathcal{O}_i^{\rm (exp)}$ 
is obtained from the central theoretical prediction 
$\mathcal{O}_i^{(\textrm{th})}$
for each bin $i$ out of $N_{\textrm{bin}}$ by fluctuating
it within its uncertainties, following either
Eq.~(\ref{eq:pseudo_data}), when accounting for the correlations
between systematic uncertainties, or Eq.~(\ref{eq:pseudo_data_v2}),
in the case in which errors are added in quadrature.

@@

\subsection{Implementation in NNPDF}

>>>>

The profiling method applied to Hessian PDF fits is described in~\cite{Paukkunen:2014zia, Schmidt:2018hvu, AbdulKhalek:2018rok, HERAFitterdevelopersTeam:2015cre} and is based
on minimizing a goodness-of-fit error function defined as
\begin{equation}
\chi^2 = 
\sum_{i=1}^{N_{\textrm{bin}}} 
\frac{\left(  \mathcal{O}_i^{\rm (exp)}
            + \Gamma_i^{\alpha,\textrm{pd}}
              b_\alpha^{\textrm{(pd)}}
            - \mathcal{O}_i^{\rm (th)}
            - \Gamma_i^{\beta,\textrm{th}}
              b_\beta^{(\textrm{th})}
     \right)^2
     }{ \left(\delta_i^{\rm stat}\right)^2 }
+ \sum_\alpha \lp b_\alpha^{(\textrm{pd})}\rp^2
+ \sum_\beta  \lp b_\beta^{\textrm{(th)}}\rp ^2 \, .
\label{eq:profilingchi2}
\end{equation}
The pseudodata 
$\mathcal{O}_i^{\rm (exp)}$ 
is obtained from the central theoretical prediction 
$\mathcal{O}_i^{(\textrm{th})}$
for each bin $i$ out of $N_{\textrm{bin}}$ by fluctuating
it within its uncertainties, following either
Eq.~(\ref{eq:pseudo_data}), when accounting for the correlations
between systematic uncertainties, or Eq.~(\ref{eq:pseudo_data_v2}),
in the case in which errors are added in quadrature.

@@

\subsection{Implementation in NNPDF}
\label{subsec:NNPDF}

### 2023-07-06 paper/sec-dis-pseudodata.tex
Removed mentions of reduction factor 0.5 which is now unnecessary, unified notation

 The central values for the LHC neutrino scattering pseudo-data, denoted
 by $\mathcal{O}_i^{{\rm exp}} $, are obtained
 by fluctuating this reference theory prediction by the statistical and systematic
 uncertainties, that is
 \begin{equation}
  \label{eq:pseudo_data}
  \mathcal{O}_i^{{\rm (exp)}}  =   \mathcal{O}_i^{{\rm (th)}}\left( 1+ r^{(i)}_{\rm stat}\delta_{i,{\rm stat}}
  + \sum_{k=E_\ell, E_h,\theta_\ell} r_{{\rm sys},k} \,\delta_{i,{\rm sys}}^{(k)}\right) \, , \qquad i=1,\ldots,N_{\rm bin} \, ,
 \end{equation}
 with $r^{(i)}_{\rm stat}$ and $r_{{\rm sys},k}$ being univariate Gaussian random numbers,
 and $\delta_{\rm stat}$ ($\delta_{\rm sys}^{(k)}$) indicate the relative statistical (systematic)
 uncertainties associated to the $i$-th bin.
 %
 Note that a given systematic variation is assumed to be fully correlated among all the bins
 in the measurement.

 Alternatively, we can add all uncertainties in quadrature and account for a possible
 improvement in the systematic errors with respect to the current estimates,
 \be
 \delta_{{\rm tot},i}^{\rm exp} = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
\left( f_{{\rm red},j}\delta_{i,j}^{\rm sys} \right)^2\right)^{1/2} \, ,
 \ee
 with $f_{{\rm red},j} \le 1$ quantifies the possible reduction of systematic uncertainties, and
 then the pseudo-data is evaluated by means of
 \begin{equation}
  \label{eq:pseudo_data_v2}
  \mathcal{O}_i^{{\rm (exp)}}  =   \mathcal{O}_i^{{\rm (th)}}\left( 1+ r^{(i)}_{\rm stat}\delta_{i,{\rm tot}}
  \right) \, , \qquad i=1,\ldots,N_{\rm bin} \, .
 \end{equation}
 While the actual correlation model will lie somewhere between no correlation and full correlation,
 these two approaches to generate the pseudo-data bracket the projected impact
 on the PDFs and its dependence on the experimental correlation model.

>>>>

 The central values for the LHC neutrino scattering pseudo-data, denoted
 by $\mathcal{O}_i^{{\rm (exp)}} $, are obtained
 by fluctuating this reference theory prediction by the statistical and systematic
 uncertainties, that is
 \begin{equation}
  \label{eq:pseudo_data}
  \mathcal{O}_i^{{\rm (exp)}}
  =   \mathcal{O}_i^{{\rm (th)}}\left( 1+ r_{i} \delta_{i}^{\rm stat}
  + \sum_{k=E_\ell, E_h,\theta_\ell}
    r'_{k} \,\delta_{i,k}^{{\rm sys}}\right) \, , \qquad i=1,\ldots,N_{\rm bin} \, ,
 \end{equation}
 with $r_{i}$ and $r'_{k}$ being univariate Gaussian random numbers,
 and $\delta_i^{\rm stat}$ ($\delta_{i,k}^{\rm sys}$) indicate the relative statistical (systematic)
 uncertainties associated to the $i$-th bin (and $k$-th source of systematic uncertainty).
 %
 Note that a given systematic variation is assumed to be fully correlated among all the bins
 in the measurement.

 Alternatively, we can add all uncertainties in quadrature and account for a possible
 improvement in the systematic errors with respect to the current estimates,
 \be
 \delta_{i}^{\rm tot}
 = \left( \left( \delta_i^{\rm stat}\right)^2 + \sum_{k=1}^{n_{\rm sys}}
\left( \delta_{i,k}^{\rm sys} \right)^2\right)^{1/2} \, ,
 \ee
 and the pseudo-data is evaluated by means of
 \begin{equation}
  \label{eq:pseudo_data_v2}
  \mathcal{O}_i^{{\rm (exp)}}
  = \mathcal{O}_i^{{\rm (th)}}
    \left( 1+ r_i \delta_i^{\rm tot}
    \right) \,
    , \qquad i=1,\ldots,N_{\rm bin} \, .
 \end{equation}
 While the actual correlation model will lie somewhere between no correlation and full correlation,
 these two approaches to generate the pseudo-data bracket the projected impact
 on the PDFs and its dependence on the experimental correlation model.
